ODGI: understanding pangenome graphs

### 2022-02-17 manuscript/main.tex
mention the supp sorting figure in the text

Pangenome graphs can hide their underlying latent structures, introducing difficulties in the analysis and interpretation. % (Fig.~\ref{fig:sorting}\textbf{a}).
Among the causes of this is the correct ordering of the graph nodes in a convenient number of dimensions.
ODGI provides a variety of sorting algorithms to find the best graph node order in 1 or 2 dimensions, allowing us
to understand the sparse structures typically found in pangenome graphs and the genetic variation they represent.

>>>>

Pangenome graphs can hide their underlying latent structures, introducing difficulties in the analysis and interpretation. % (Fig.~\ref{fig:sorting}\textbf{a}).
Among the causes of this is the correct ordering of the graph nodes in a convenient number of dimensions.
ODGI provides a variety of sorting algorithms to find the best graph node order in 1 or 2 dimensions, allowing us
to understand the sparse structures typically found in pangenome graphs and the genetic variation they represent \REVIEWED{(Figure~\ref{fig:sorting})}.
